\subsection{A6}\label{A6}

Due to situations listed above, we need to consider key items when handling the data:
\begin{itemize}
    \item privacy
    \begin{itemize}
        \item Users need to be able to see and remove all their data upon request. GDPR \parencite{voigt2017eu} is a great example of how users data can be protected
    \end{itemize}

    \item honesty
    \begin{itemize}
        \item Use of cookies or tracking the user should be easily identifiable and configurable (option to turn off) \parencite{englehardt2015cookies}
        \item Data breaches are not 100\% avoidable, therefore if anything happens it needs to be transparent with the users \parencite{sen2015estimating}
        \item If users data is collected (sold), they need to be aware of it
    \end{itemize}

    \item security
    \begin{itemize}
        \item sensitive data needs to be encrypted in case of the data breach \parencite{smid1988data}
        \item when dealing with sensitive data, employees need to have proper clearance and security checks done. The best approach would be to use least privilege rule, meaning that data would be on need to know bases. Since this could represent a problem for development environment, that can have a copy of production but with fake data instead
    \end{itemize}

    \item moral
    \begin{itemize}
        \item when working with data, we need to know when something could hurt someone. As mentioned above, the twitter data can be used for malicious purpose. Due to situations like this, we need to ask ourselves, what does it bring to the company? It can help with advertisements but it can also help with harassment. In this case, if we need Twitter data, we can store it but not make it visible to other players.
    \end{itemize}
\end{itemize}