\section{Exploratory data analysis}\label{EDA}

Exploratory data analysis (EDA) is a process in which we familiarise ourselves with data \parencite{tukey1977exploratory}. Listed in the tree structure bellow are the files originally provided to us. Listed bellow can be seen split sections, based on the nested paths (chat, combined and flamingo data).

\dirtree{%
.1 DataSet.
.2 dataset\_attribute\_desc.doc.
.3 description of the dataset.
.2 combined-data.csv.
.2 chat-data.
.3 chat\_join\_team\_chat.csv.
.4 When a user joins a team, a new record is going to be added to this file. 
.3 chat\_leave\_team\_chat.csv.
.4 When a user leaves a team, a new record is going to be added to this file. 
.3 chat\_mention\_team\_chat.csv.
.4 When a user gets a mention, a new record is going to be added to this file. 
.3 chat\_respond\_team\_chat.csv.
.4 When a player with chatid2 responds to a post by another player with chatid2, a new line is added in this file.
.2 flamingo-data.
.3 ad-clicks.csv.
.4 Database of clicks on ads.
.3 buy-clicks.csv.
.4 Database of purchases.
.3 game-clicks.csv.
.4 A record of each click a user performed during the game.
.3 level-events.csv.
.4 A record of each level event for a teams,lLevel events are recorded when a team ends or begins a new level.
.3 team-assignments.csv.
.4 A record of each time a user joins a team.
.3 team.csv.
.4 A record of each team in the game.
.3 user-session.csv.
.4 A record of each session a user plays.
.3 users.csv.
.4 Database of the game users.
}

Originally the following items were zipped:
\begin{itemize}
    \item chat-data.zip
    \item combined-data.zip
    \item flamingo-data.zip
\end{itemize}


\input{Sections/EDA/CombinedData/combinedData.tex}
\input{Sections/EDA/ChatData/ChatData.tex}
\input{Sections/EDA/FlamingoData/flamingoData.tex}